Simulations of gravity-driven flow of binary liquids in microchannels

### 2011-04-06 Text/paper.tex
Minor style corrections.

\newcommand{\Ca}{\mathrm{Ca}}
\newcommand{\todo}[1]{{\color{red}#1}}

@@

\section{Introduction}
The Taylor/Bretherton \cite{bretherton} flow deals with long gas bubbles moving through liquid in
narrow channels, Fig. \ref{fig:classical:bretherton}. It was found that the front meniscus film
thickness is proportional
to $\Ca^{2/3}$ for capillary numbers smaller than $0.003$, where the capillary number is defined as:
\begin{equation}
\label{capillary:number:definition}
\Ca=\frac{\mu_\mathrm{liq} U_\mathrm{bubble}}{\gamma},
\end{equation}
where $\mu_{liq}$ is the liquid viscosity, $U_{bubble}$ is the bubble velocity, and
$\gamma$ is the interfacial tension between gas and liquid.
\begin{figure}
\includegraphics[width=\textwidth]{Figures/benchmark_bretherton.eps}
\caption{The classical Bretherton problem layout. The gas bubble
propagates with the steady velocity $U_{\mathrm{bubble}}$ through the liquid media and deposits
the film, where thickness to the height of the channel $H_{\mathrm{eff}}$ ratio is 
$\delta$.\label{fig:classical:bretherton}} 
\end{figure}

While there are many works which simulate the Bretherton problem by the boundary value approach
\cite{ingham-plates,heil-bretherton}, those methods are of limited applicability for problems
involving complex geometries, free interface motion, or for problems involving coalescence and/or
droplet breakup. The continuous interface models are more flexible for those kinds of simulations.
However, if the interface is smeared out over several grid nodes, the question of
proper film resolution in comparison with the interface resolution arises.  This work is focused on
exploring the parameter range of the binary liquid lattice
Boltzmann method to resolve correctly the flow in a range of capillary numbers.

@@

The binary liquid free-energy LB model due to \citet{swift} we used
simulates two liquids with the assumption of uniform overall
density. While the classical Bretherton problem is stated for gas and liquid, which are of
significantly
different densities and viscosities, it was indicated \cite{bretherton} that inertia effects were
negligible. Moreover, the results of \citet{giavedoni-numerical} and \citet{heil-bretherton} show
{\color{red} insignificant} Reynolds number effects on the film thickness for a relatively wide
range of Reynolds
numbers. 
{\color{red} For example, \citet{giavedoni-numerical} suggested that the Reynolds number effects
are negligible for $\Ca\leq0.05$ and have moderate changes for $\Ca>0.05$ in the range of Reynolds
number from $0$ to $70$. Later on, \citet{heil-bretherton} extended results upto Reynolds number
$300$. The indicate that while the influence of the established film thickness is insignificant
($7$ percent from the film thickness measured at $Re=0$). However, the Reynolds number influence
significantly the pressure distrubution and the flow field near the front bubble tip. In the present
simulations the largest Reynolds number we achieve is less than $20$ and it allows to neglect 
inertia effects.} 
Therefore, the major governing parameter for microchannel Bretherton flows is not the density ratio,
but the
viscosity ratio. Moreover, the results based on uniform density, as in the case of the LBM
binary liquid model, are in good agreement with other simulations
\cite{giavedoni-numerical,heil-bretherton} in which inertia effects were taken into account.

@@

One should acknowledge the work of \citet{pagonabarraga-fingers} on menisci
in thin films for fingering phenomena. \citet{sehgal-microchannel} performed lattice Boltzmann
simulations of two-dimensional channel flows for relatively large capillary numbers, and
found discrepancies with the classical Bretherton theory, which
is limited to the low capillary number regime \cite{giavedoni-numerical}. These authors didn't take
into
the account recent studies extending microchannel simulations for the capillary numbers
beyond the Bretherton regime. Thus, the comparison with other established CFD methods is limited.
\citeauthor{sehgal-microchannel} used the Shan-Chen model \cite{Shan-chen:extended} to simulate the
multiphase behavior. It is also
the continuous interface model, but the study of grid dependence is absent.

{\color{red}
Level set method is represented by a number of works \cite{fukugata-levelset,
lakehal-micro, carlson-comparison}. While the bubble shapes  were found in a good agreeement
with the experiments, the range of studied bubble lengths is confined to $2-3$ channels diameters.
Thus, the bubble radius changes significantly and cannot be used as classical Bretherton problem
benchmark. However, the works provide insight to the bubble formation and to the way small bubbles
flow in the
microchannels.}

\section{Lattice Boltzmann binary liquid model}
The lattice Boltzmann equation (LBE) operates on a rectangular grid representing the
physical domain. It utilizes
probability distribution functions (also known as particle populations)
containing information about
macroscopic variables, such as fluid density and momentum. LBE consists of
two parts: a local collision step, and a propagation step which transports
information from one node to another along some 
directions specified by the discrete velocity set.
The LBE is typically implemented as follows:
\begin{equation}
\label{standard:implementation}
\begin{aligned}
&f_i^{*}(\bm{x},t)=\omega f_i^{eq}(\bm{x},t)-(1-\omega) f_i(\bm{x},t) +
F_i,&&\text{ collision step}\\
&f_i(\bm{x}+\bm{c_i},t+1)=f_i^{*}(\bm{x},t),&&\text{ propagation step}, 
\end{aligned}
\end{equation}
where $f_i$ is the probability distribution function in the direction $\bm{c_i}$,
{\color{red} $f_i^{eq}$ is the equilibrium probability distribution function}, $\omega$ is the
relaxation parameter, and $F_i$ is the external force population.{\color{red} The force population
is connected with the force and is implemented in the current work due to work \cite{guo}.}

@@

{\color{red}
While the lattice Boltzmann system has parameters as gas and liquid
viscosities, the surface tension, etc., those parameters are not the representative and
proportional quantities of the parameters in a physical system. The parameters of the lattice
Boltzmann are connected with the physical world's parameters only through the non-dimensional
numbers governing the physics of the problem. In this case it is a capillary number $\Ca$ and a
viscosity ratio $\frac{\mu_{\mathrm{liq}}}{\mu_{\mathrm{gas}}}$, which are
obtained from the physical world and then they are matched through the lattice Boltzmann quantities.
 The set of
the fluid and phase equations \eqref{binary:fluid:system} is valid in the lattice Boltzmann space
and in the physical domain. Therefore, one can substitute any quantity, i.e.
$U_{\mathrm{bubble}}$, in the physical units or in the lattice Boltzmann units as soon as the
capillary number is the same in both worlds.}

@@

\section{Approach to benchmark}

@@

implies that we can use the periodic boundary conditions in the streamwise direction. As soon as the

@@

\section{Results}
\subsection{The nondimensionalization and initialization procedure}
\label{section:init}
We now introduce the procedure of nondimensionalization, as well as
the initialization technique we used to determine the parameters necessary for
the simulation. The capillary number defined in Eq.~\ref{capillary:number:definition} governs the
interface thickness.
%The bubble velocity $U_{\mathrm{bubble}}$ is taken in the center of the bubble where the film
%thickness is examined.
{\color{red} Parameters as $\mu_{\mathrm{liq}}$, $\gamma$ are usually taken in the already defined
stable range. The capillary number $\Ca$ is supplied from the physical world.} 
In comparison, the bubble
velocity $U_{\mathrm{bubble}}$ is not given
explicitly.
In our simulations we approximate $U_{\mathrm{bubble}}$ with the
Poiseuille profile maximum velocity, which is given as:
\begin{equation}
\begin{aligned}
&U_{\mathrm{bubble}} \approx \frac{H_{\mathrm{eff}}^2}{8
\mu_{\mathrm{liq}}}\frac{\mathrm{d}P}{\mathrm{d}x}\\
&U_{\mathrm{bubble}}\approx
\frac{{(N_y-2)}^2}{\frac{8}{6}(\tau_{\mathrm{liq}}-\frac{1}{2})}\frac{\mathrm{d}P}{\mathrm{d}
x } ,
\end{aligned}
\end{equation}
where $N_y$ is the number of nodes in the vertical direction. As will be discussed further, the
effective channel width is defined as $H_{\mathrm{eff}}=N_y-2$ because of bounce-back nodes to
mimic no-slip conditions at the walls.
For the Poiseuille profile one can estimate the body force (pressure gradient) through the
capillary number and grid resolution:
\begin{equation}
\label{poiseuille:velocity:center}
\begin{aligned}
&\frac{\mathrm{d}P}{\mathrm{d}x}=\frac{8}{{(N_y-2)}^2}\gamma \Ca.
\end{aligned}
\end{equation}
In the simulations the body force (\ref{poiseuille:velocity:center}) causes the bubble
velocity to differ from that implied by the Poiseuille relation because of the bubble presence in a
flow. That is
why an iteration procedure is needed to achieve the 
desired velocity and 
capillary number. 
However, the initialization body force as given by (\ref{poiseuille:velocity:center}) is a good
starting point.

@@

interface thickness is spread over approximately $5$ lattice units. The study of the interface

@@

 \item[Velocity] The relaxation parameters are taken to be in the stable range for hte simulations.

@@

{\color{red}
Note that the initialization procedure is a good guide of designing the simulations. For example
for the grid refinement, Section \ref{section:grid:refinement}, we keep the same velocity
$U_{\mathrm{bubble}}$ and $\Ca$. This implies the conservation of the quantity
$H_{\mathrm{eff}}^2\frac{\mathrm{d}P}{\mathrm{d}x}=(N_y-2)^2\frac{\mathrm{d}P}{\mathrm{d}
x } = \mathrm{const}$. For designing capillary range simulations, Section
\ref{section:capillary:range}, we use a proportionality law to initialize body forces knowing
results of just one simulation:
\begin{equation}
\begin{aligned}
&\Ca_{\mathrm{lit}} \propto U_{\mathrm{bubble}}\\
&U_{\mathrm{bubble}} \propto \frac{\mathrm{d}P}{\mathrm{d}x} H_{\mathrm{eff}}^2\\
&\Ca_{\mathrm{lit}} \propto \frac{\mathrm{d}P}{\mathrm{d} x} H_{\mathrm{eff}}^2 \text{ or }\\
&\frac{\mathrm{d}P}{\mathrm{d} x} \propto \frac{\Ca_{\mathrm{lit}}}{H_{\mathrm{eff}}^2},
\end{aligned}
\end{equation}
where the subscript ,,lit'' stands for the predicted capillary number
\cite{giavedoni-numerical,heil-bretherton}. 
}
{\color{red}
\subsection{Steady state}
\label{sec:steady:state}
The simulations were performed in order to determine the number of iterations for the bubble to
reach the steady state. The grid was chosen as $202 \times 3000$. The body force was $0.375\times
10^{-6}$. The initial film thickness was taken as $12$ nodes. Table \ref{table:steady:state}
summarizes the simulation results in terms of the film thickness in the middle of the bubble and the
velocity of the interface. We can conclude it is enough to have $100000-300000$ iterations for
bubble to approach the steady state.
\begin{table}
\begin{tabularx}{\textwidth}{|X|X|X|X|X|X|X|}
\hline
$N_\mathrm{iter}$&$\delta$&$U_{\mathrm{bubble}}$&{\color{red} $Re$}\\
\hline
$10000$&$ 0.0655$&$0.0027$&$0.81$\\
\hline
$14000$&$0.0608$&$0.0027$&$0.81$\\
\hline
$18000$&$0.0577$&$0.0027$&$0.81$\\
\hline
$22000$&$0.0630$&$0.0027$&$0.81$\\
\hline
$26000$&$0.0660$&$0.0027$&$0.81$\\
\hline
$30000$&$0.0661$&$0.0027$&$0.81$\\
\hline
\end{tabularx}
\caption{The results for steady-state calculations. The simulated domain is
of size $202 \times 3000$. $U_{\mathrm{bubble}}$ is the velocity of the interface at the fron tip of
the bubble. $\Ca=0.05$ was taken to initialize the simulation. One can see that in terms of
velocities and film thicknesses $100000-300000$ iterations are enough.
\label{table:steady:state}}
\end{table}
}

@@

\citet{giavedoni-numerical} showed that the film stabilizes at the distances as $2.6-4.0$ diameters

@@

\citet{heil-bretherton} was extracted by hands using a set of curves involving interpolation and
it's the reason for a data to exhibit a noisy trend.} \label{fig:capillary:comparison}}

@@

{\color{red} Also, while it is necessary to increase the viscosities ratio for the binary-liquid
formulation to be close to the physical Bretherton formulation, one needs to be attentive to the
numerical accuracy of the LBM formulation. It is known \cite{ginzburg-trt-simple-hydro} that the
BGK collision operator used in the present scheme has residual error accuracy proportional
to $\Bigl(\tau-\frac{1}{2}\Bigr)^2$. That means that by increasing the viscosity one reduces the
spatial
accuracy of the method. To avoid this one needs to use advanced formulations of the LBM collision
operator, as two-relaxation-times (TRT) and multiple-relaxation-times (MRT) collision operators
\cite{ginzburg-main}. Although TRT and MRT collisions operators are studied for simple
hydrodynamics solutions, their application to complex fluid flows is sparse and not studied
well.
}
\begin{figure}
\includegraphics[width=\textwidth]{Figures/Capillary_Viscous/capillaries_viscous.eps}
\caption{The film thicknesses versus capillary number for
$\frac{\mu_{\mathrm{liq}}}{\mu_{\mathrm{gas}}}=10$ and $\frac{\mu_{\mathrm{liq}}}{\mu_{\mathrm{gas}}}=20$. \label{fig:capillary:viscous}}
\end{figure}

>>>>

\newcommand{\Ca}{\mathrm{Ca}}
\renewcommand{\Re}{\mathrm{Re}}
\newcommand{\todo}[1]{{\color{red}#1}}

@@

\section{Introduction}
The Taylor/Bretherton \cite{bretherton} flow deals with long gas bubbles moving through liquid in
narrow channels, Fig. \ref{fig:classical:bretherton}. It was found that the front meniscus film
thickness is proportional
to $\Ca^{2/3}$ for capillary numbers smaller than $0.003$, where the capillary number is defined as:
\begin{equation}
\label{capillary:number:definition}
\Ca=\frac{\mu_\mathrm{liq} U_\mathrm{bubble}}{\gamma},
\end{equation}
where $\mu_{liq}$ is the liquid viscosity, $U_{bubble}$ is the bubble velocity, and
$\gamma$ is the interfacial tension between gas and liquid.
\begin{figure}
\includegraphics[width=\textwidth]{Figures/benchmark_bretherton.eps}
\caption{The classical Bretherton problem layout. The gas bubble
propagates with the steady velocity $U_{\mathrm{bubble}}$ through the liquid media and deposits
the film, where the thickness to height of the channel $H_{\mathrm{eff}}$ ratio is 
$\delta$.\label{fig:classical:bretherton}} 
\end{figure}

While there are many works which simulate the Bretherton problem by the boundary value approach
\cite{ingham-plates,heil-bretherton}, those methods are of limited applicability for problems
involving complex geometries, free interface motion, or coalescence and/or
droplet breakup. The continuous interface models are more flexible for those kinds of simulations.
However, if the interface is smeared out over several grid nodes, the question of
proper film resolution in comparison with the interface resolution arises.  This work is focused on
exploring the parameter range of the binary liquid lattice
Boltzmann method to resolve correctly the flow in a range of capillary numbers.

@@

The binary liquid free-energy LB model due to \citet{swift} we used
simulates two liquids with the assumption of uniform overall
density. While the classical Bretherton problem is stated for gas and liquid, which are of
significantly
different densities and viscosities, it was indicated \cite{bretherton} that inertia effects were
negligible. Moreover, the results of \citet{giavedoni-numerical} and \citet{heil-bretherton} show
{\color{red} insignificant} Reynolds number ($\Re$) effects on the film thickness for a relatively wide
range of Reynolds
numbers. 
{\color{red} For example, \citet{giavedoni-numerical} suggested that the Reynolds number effects
are negligible for $\Ca\leq0.05$ and have moderate impact for $\Ca>0.05$ in the range of Reynolds
number from $0$ to $70$. Later on, \citet{heil-bretherton} extended these results up to
$\Re = 300$. This indicates that while the Reynolds number influence on the established film thickness is insignificant
($7$ percent from the film thickness measured at $\Re=0$), the pressure distribution and the flow field near the front bubble tip
can be affected by changes in $\Re$.  Since in the present work we only deal with flows with $\Re < 20$, we can safely
neglect any inertia effects and conclude that the major governing parameter for microchannel Bretherton flows is not the density ratio,
but the
viscosity ratio}. Moreover, the results based on uniform density, as in the case of the LBM
binary liquid model, are in good agreement with other simulations
\cite{giavedoni-numerical,heil-bretherton} in which inertia effects were taken into account.

@@

One should acknowledge the work of \citet{pagonabarraga-fingers} on menisci
in thin films for fingering phenomena, as well as the work of \citet{sehgal-microchannel} who
performed lattice Boltzmann
simulations of two-dimensional channel flows for relatively large capillary numbers, and
found discrepancies with the classical Bretherton theory, which
is limited to the low capillary number regime \cite{giavedoni-numerical}. These authors did not take
into
account recent studies extending microchannel simulations for the capillary numbers
beyond the Bretherton regime. Thus, the comparison with other established CFD methods is limited.
\citeauthor{sehgal-microchannel} used the Shan-Chen model \cite{Shan-chen:extended} to simulate the
multiphase behavior. The Shan-Chen model is also a
continuous interface model, but the above-mentioned paper does not contain a study of grid dependence.

{\color{red}
The level set method is also represented by a number of works \cite{fukugata-levelset,
lakehal-micro, carlson-comparison}. While the bubble shapes  were found to be in a good agreement
with the experiments, the range of studied bubble lengths is confined to $2-3$ channel diameters.
Thus, the bubble radius changes significantly and cannot be used as a classical Bretherton problem
benchmark. However, the works provide insight to the bubble formation and to the way small bubbles
flow in the
microchannels.}

\section{Lattice Boltzmann binary liquid model}
The lattice Boltzmann equation (LBE) operates on a rectangular grid representing the
physical domain. It utilizes
probability distribution functions (also known as particle populations)
containing information about
macroscopic variables, such as fluid density and momentum. LBE consists of
two parts: a local collision step, and a propagation step which transports
information from one node to another along some 
directions specified by the discrete velocity set.
The LBE is typically implemented as follows:
\begin{equation}
\label{standard:implementation}
\begin{aligned}
&f_i^{*}(\bm{x},t)=\omega f_i^{eq}(\bm{x},t)-(1-\omega) f_i(\bm{x},t) +
F_i,&&\text{ collision step}\\
&f_i(\bm{x}+\bm{c_i},t+1)=f_i^{*}(\bm{x},t),&&\text{ propagation step}, 
\end{aligned}
\end{equation}
where $f_i$ is the probability distribution function in the direction $\bm{c_i}$,
{\color{red} $f_i^{eq}$ is the equilibrium probability distribution function}, $\omega$ is the
relaxation parameter, and $F_i$ is the external force population. {\color{red} The force population
is represents an texternal physical force and is implemented in the current work using the scheme
outlined in \citet{guo}.}

@@

{\color{red}
While the lattice Boltzmann system has parameters such as the surface tension, the gas and liquid
viscosities, etc., those parameters are not the representative and
proportional quantities of the parameters in a physical system. The parameters of the lattice
Boltzmann are connected with the physical world's parameters only through the non-dimensional
numbers governing the physics of the problem. In our case, these numbers are the capillary number $\Ca$ and the
viscosity ratio $\frac{\mu_{\mathrm{liq}}}{\mu_{\mathrm{gas}}}$, which are
obtained from the physical world and then matched through the lattice Boltzmann quantities.
 The set of
the fluid and phase equations \eqref{binary:fluid:system} is valid in the lattice Boltzmann space
and in the physical domain. Therefore, one can substitute any quantity, i.e.
$U_{\mathrm{bubble}}$, in the physical units or in the lattice Boltzmann units as soon as the
capillary number is the same in both worlds.}

@@

\section{Numerical benchmark procedure}

@@

implies that we can use periodic boundary conditions in the streamwise direction. As soon as the

@@

\section{Results}
\subsection{The nondimensionalization and initialization procedure}
\label{section:init}
We now introduce the procedure of nondimensionalization, as well as
the initialization technique we used to determine the parameters necessary for
the simulation. The capillary number defined in Eq.~\ref{capillary:number:definition} governs the
interface thickness.
%The bubble velocity $U_{\mathrm{bubble}}$ is taken in the center of the bubble where the film
%thickness is examined.
{\color{red} Parameters as $\mu_{\mathrm{liq}}$, $\gamma$ are usually taken in the already defined
stable range. The capillary number $\Ca$ is supplied from the physical world.} 
In comparison, the bubble
velocity $U_{\mathrm{bubble}}$ is not given
explicitly.
In our simulations we approximate $U_{\mathrm{bubble}}$ with the
Poiseuille profile maximum velocity, which is given as:
\begin{equation}
\begin{aligned}
&U_{\mathrm{bubble}} \approx \frac{H_{\mathrm{eff}}^2}{8
\mu_{\mathrm{liq}}}\frac{\mathrm{d}P}{\mathrm{d}x}\\
&U_{\mathrm{bubble}}\approx
\frac{{(N_y-2)}^2}{\frac{8}{6}(\tau_{\mathrm{liq}}-\frac{1}{2})}\frac{\mathrm{d}P}{\mathrm{d}
x } ,
\end{aligned}
\end{equation}
where $N_y$ is the number of nodes in the vertical direction. As will be discussed further, the
effective channel width is defined as $H_{\mathrm{eff}}=N_y-2$ due to the use of bounce-back nodes to
mimic no-slip conditions at the walls.
For the Poiseuille profile one can estimate the body force (pressure gradient) through the
capillary number and grid resolution:
\begin{equation}
\label{poiseuille:velocity:center}
\begin{aligned}
&\frac{\mathrm{d}P}{\mathrm{d}x}=\frac{8}{{(N_y-2)}^2}\gamma \Ca.
\end{aligned}
\end{equation}
In the simulations the body force (\ref{poiseuille:velocity:center}) causes the bubble
velocity to differ from that implied by the Poiseuille relation because of the presence of a bubble in the
flow. That is
why an iterative procedure is needed to achieve the 
desired velocity and 
capillary number. 
However, the initial body force as given by (\ref{poiseuille:velocity:center}) is a good
starting point.

@@

interface is spread over approximately $5$ lattice units. The study of the interface

@@

 \item[Velocity] The relaxation parameters are taken to be in the stable range for the simulations.

@@

{\color{red}
Note that the initialization procedure is a good guide of designing the simulations. For example
for the grid refinement, Section \ref{section:grid:refinement}, we keep the same velocity
$U_{\mathrm{bubble}}$ and $\Ca$. This implies the conservation of the quantity
$H_{\mathrm{eff}}^2\frac{\mathrm{d}P}{\mathrm{d}x}=(N_y-2)^2\frac{\mathrm{d}P}{\mathrm{d}
x } = \mathrm{const}$. For designing capillary range simulations, Section
\ref{section:capillary:range}, we use a proportionality law to initialize body forces knowing
results of just one simulation:
\begin{equation}
\begin{aligned}
&\Ca_{\mathrm{lit}} \propto U_{\mathrm{bubble}}\\
&U_{\mathrm{bubble}} \propto \frac{\mathrm{d}P}{\mathrm{d}x} H_{\mathrm{eff}}^2\\
&\Ca_{\mathrm{lit}} \propto \frac{\mathrm{d}P}{\mathrm{d} x} H_{\mathrm{eff}}^2 \text{ or }\\
&\frac{\mathrm{d}P}{\mathrm{d} x} \propto \frac{\Ca_{\mathrm{lit}}}{H_{\mathrm{eff}}^2},
\end{aligned}
\end{equation}
where the subscript ,,lit'' stands for the predicted capillary number
\cite{giavedoni-numerical,heil-bretherton}. 
}
{\color{red}
\subsection{Steady state}
\label{sec:steady:state}
The simulations were performed in order to determine the number of iterations for the bubble to
reach the steady state. The grid was chosen as $202 \times 3000$. The body force was $0.375\times
10^{-6}$. The initial film thickness was taken as $12$ nodes. Table \ref{table:steady:state}
summarizes the simulation results in terms of the film thickness in the middle of the bubble and the
velocity of the interface. We can conclude it is enough to have $100000-300000$ iterations for
the bubble to approach the steady state.
\begin{table}
\begin{tabularx}{\textwidth}{|X|X|X|X|X|X|X|}
\hline
$N_\mathrm{iter}$&$\delta$&$U_{\mathrm{bubble}}$&{\color{red} $\Re$}\\
\hline
$10000$&$ 0.0655$&$0.0027$&$0.81$\\
\hline
$14000$&$0.0608$&$0.0027$&$0.81$\\
\hline
$18000$&$0.0577$&$0.0027$&$0.81$\\
\hline
$22000$&$0.0630$&$0.0027$&$0.81$\\
\hline
$26000$&$0.0660$&$0.0027$&$0.81$\\
\hline
$30000$&$0.0661$&$0.0027$&$0.81$\\
\hline
\end{tabularx}
\caption{The results for steady-state calculations. The simulated domain is
of size $202 \times 3000$. $U_{\mathrm{bubble}}$ is the velocity of the interface at the fron tip of
the bubble. $\Ca=0.05$ was taken to initialize the simulation. One can see that in terms of
velocities and film thicknesses $100000-300000$ iterations are enough.
\label{table:steady:state}}
\end{table}
}

@@

\citet{giavedoni-numerical} showed that the film stabilizes at the distances of $2.6-4.0$ diameters

@@

\citet{heil-bretherton} was extracted manuallys using a set of curves involving interpolation and
is the reason while the data exhibits a noisy trend.} \label{fig:capillary:comparison}}

@@

{\color{red} Also, while it is necessary to increase the viscosities ratio for the binary-liquid
formulation to be close to the physical Bretherton formulation, one needs to be attentive to the
numerical accuracy of the LBM formulation. It is known \cite{ginzburg-trt-simple-hydro} that the
BGK collision operator used in the present scheme has residual error accuracy proportional
to $\Bigl(\tau-\frac{1}{2}\Bigr)^2$. That means that by increasing the viscosity one reduces the
spatial
accuracy of the method. To avoid this one needs to use advanced formulations of the LBM collision
operator, such as two-relaxation-times (TRT) and multiple-relaxation-times (MRT) collision operators
\cite{ginzburg-main}. Although TRT and MRT collisions operators are studied for simple
hydrodynamics solutions, their application to complex fluid flows is sparse and not studied
well.
}
\begin{figure}
\includegraphics[width=\textwidth]{Figures/Capillary_Viscous/capillaries_viscous.eps}
\caption{The film thicknesses versus capillary number for
$\frac{\mu_{\mathrm{liq}}}{\mu_{\mathrm{gas}}}=10$ and $\frac{\mu_{\mathrm{liq}}}{\mu_{\mathrm{gas}}}=20$. \label{fig:capillary:viscous}}
\end{figure}
